Pre Processing of the Long Term Data

### 2018-05-27 scripts/1_str_preprocessing.Rmd
Update ltr prep.

  # Add nested daily data to structural data
  str_df <- str_df %>%
    as.tibble() %>%
    left_join(daily_tdf, by='property_id')

@@

 dir.create(file.path(getwd(), 'data', 'prepared'))
 saveRDS(str_df, file=file.path(getwd(), 'data', 'prepared', 'str_data.RDS'))

>>>>

  # Add nested daily data to structural data
  str_tdf <- str_df %>%
    as.tibble() %>%
    left_join(daily_tdf, by='property_id')

@@

 dir.create(file.path(getwd(), 'data', 'prepared'))
 saveRDS(str_tdf, file=file.path(getwd(), 'data', 'prepared', 'str_data.RDS'))

### 2018-05-27 scripts/2_ltr_preprocessing.Rmd
Update ltr prep.

---
title: "Pre Processing of the Long Term Data"
author: "Andy Krause"
date: "April 14, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script executes a number of long running data preparation process necessary to analyze the long term rental data.  If you re-knit (with RMarkdown) this file the code will not evaluate.  To actually evaluate the code you must manually re-run the code chunks

```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

@@

We begin by setting stringsAsFactors to FALSE to avoid unnecessary factor conversions

@@

  library(plyr)
  library(stringr)
  library(lubridate)
  library(dplyr)
  library(multidplyr)
  library(tidyr)
  library(tibble)
  library(magrittr)

@@

We then set the paths to the data

@@

  # Assign path based on computer name
  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
  code_path <- file.path('c:', 'code', 'research', 'airBNBmelbourne')

  ## Load sources
  source(file.path(code_path, 'functions', "abb_Functions.R"))

@@

Finally, we set the date of analysis (Sept 1, 2015) to help limit the data size

@@

Next, we load the data.

@@

  # Load the raw rent data
  ltr_df <- read.csv(file.path(data_path, 'raw', 'rentData.csv'), header=T)

@@

  names(ltr_df) <- tolower(names(ltr_df))

  ltr_df <- ltr_df %>%
    dplyr::select(geo_id=geographicalid, event_id=eventid, 
                  addr_id=addressid, activity_id=activityid, flat_nbr=flatnumber,
                  str_nbr=streetnumber, str_name=streetname, str_type=streettype, 
                  suburb, postcode, latitude=property_latitude,
                  longitude=property_longitude, str_latitude=street_centroid_latitude,
                  str_longitude=street_centroid_longitude,
                  date=eventdate, price=eventprice,
                  first_date=firstadvertisedeventdate,
                  first_price=firstadvertisedeventprice, 
                  last_date=lastadvertisedeventdate,
                  last_price=lastadvertisedeventprice,property_type=propertytype, 
                  area_size=areasize, bedrooms, baths, parking, has_study=hasstudy, 
                  has_courtyard=hascourtyard, has_balcony=hasbalcony, 
                  has_ac=hasairconditioning, has_garage=hasgarage)

@@

A small portion of the observations are missing the necessary identification fields to proceed.  These are removed here.

@@

  ltr_df$last_date <- apmFixDates(ltr_df$last_date)
  ltr_df$first_date <- apmFixDates(ltr_df$first_date)
  ltr_df$date <- apmFixDates(ltr_df$date)

@@

Next, we create a unique identifier for each rental transaction.  Note that there are still, often, multiple observation per transaction due to the listing change data.

```{r uniq_trans}

 ## Create Unique Key

@@

Next, we split the data into property specific information and transasction specific information and carry out individual preparation on each (and will re-combine later)

@@

```{r}

@@

```{r}

@@

```{r}

@@

```{r}

@@

```{r}

@@

```{r}

 saveRDS(ltr_tdf, file=file.path(data_path, 'prepared', 'ltr_data.RDS'))

>>>>

---
title: "Pre Processing of the Long Term Data"
author: "Andy Krause and Gideon Aschwanden"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
editor_options: 
  chunk_output_type: console
---

This script executes a number of long running data preparation process necessary to analyze the long term rental data.  If you re-knit this file (with RMarkdown) the code will not evaluate.  To actually evaluate the code you must manually re-run the code chunks in RStudio.

```{r setup, include=FALSE}

  knitr::opts_chunk$set(echo = TRUE, eval=FALSE)

@@

We begin by setting stringsAsFactors to FALSE to avoid unnecessary factor conversions.

@@

  library(plyr)
  library(stringr)
  library(lubridate)
  library(dplyr)
  library(multidplyr) # Note you have to install from the github site hadley/multidplyr
  library(tidyr)
  library(tibble)
  library(magrittr)

@@

We then load the custom functions.

@@

  source(file.path(getwd(), 'functions', "abb_Functions.R"))

@@

Finally, we set the date of analysis (Sept 1, 2015) to help limit the data size.

@@

Next, we load the long term rental data.

@@

  ltr_df <- read.csv(file.path(getwd(), 'data', 'raw', 'ltr_data.csv'), header=T)

@@

  # Convert to lower case
  names(ltr_df) <- tolower(names(ltr_df))

  # Trim Fields
  ltr_df <- ltr_df %>%
    dplyr::select(geo_id=geographicalid, event_id=eventid, 
                  addr_id=addressid, activity_id=activityid, flat_nbr=flatnumber,
                  str_nbr=streetnumber, str_name=streetname, str_type=streettype, 
                  suburb, postcode, latitude=property_latitude,
                  longitude=property_longitude, str_latitude=street_centroid_latitude,
                  str_longitude=street_centroid_longitude,
                  date=eventdate, price=eventprice,
                  first_date=firstadvertisedeventdate,
                  first_price=firstadvertisedeventprice, 
                  last_date=lastadvertisedeventdate,
                  last_price=lastadvertisedeventprice,property_type=propertytype, 
                  area_size=areasize, bedrooms, baths, parking, has_study=hasstudy, 
                  has_courtyard=hascourtyard, has_balcony=hasbalcony, 
                  has_ac=hasairconditioning, has_garage=hasgarage)

@@

A small portion of the observations are missing the necessary identification fields (Event, Address or Activity ID) to proceed.  These are removed.

@@

  ltr_df$last_date <- fixAPMDates(ltr_df$last_date)
  ltr_df$first_date <- fixAPMDates(ltr_df$first_date)
  ltr_df$date <- fixAPMDates(ltr_df$date)

@@

Next, we create a unique identifier (by market transaction, not by observation in the data) for each rental transaction.  Note that there are still, often, multiple observations per transaction due to the listing change data. 
```{r uniq_trans}

@@

Next, we split the data into property specific information and transaction specific information and carry out individual preparation on each (and will re-combine later).

@@

```{r rec_trans}

@@

```{r rec_prop_1}

@@

```{r rec_prop_2}

@@

```{r merge_loc_prop}

@@

```{r merge_prop_trans}

@@

```{r write_out}

 dir.create(file.path(getwd(), 'data', 'prepared'))
 saveRDS(ltr_tdf, file=file.path(getwd(), 'data', 'prepared', 'ltr_data.RDS'))
